Global spirals in self-gravitating dead zones in protoplanetary discs

### 2014-10-23 paper/results.tex
new figs

\begin{figure}
  \begin{center}
    \subfigure[ZEUS-MP]{
      \includegraphics[scale=0.33]{figures/polarxy_dens015_zeus}
    }
    \subfigure[PLUTO]{
      \includegraphics[scale=0.33]{figures/polarxy_dens015_zeus}
    }
  \end{center}
  \caption{Preliminary 3D simulations using the (a) ZEUS-MP and (b)
    PLUTO. The non-axisymmetric midplane density at the end of the run
    is shown. Here $\psi \equiv \pi/2 - \theta$ is the angular height
    from the midplane.\label{3d_prelim}}   
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.41,clip=true,trim=0cm 1.75cm 0cm 0cm]{figures/nonaxi_evol_ang_zeus}
  \includegraphics[scale=0.41]{figures/nonaxi_evol_ang_zeus}
  \caption{Evolution of angular momentum components in the 3D 
    simulations show in Fig. \ref{3d_prelim}. The perturbation
    relative to $t=10P_0$ is shown in units of the initial total
    angular momentum $J_\mathrm{ref}$.\label{3d_prelim_angmom}} 
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \subfigure[ZEUS-MP]{
      \includegraphics[scale=0.33]{figures/polarxy_dens015_zeus}
    }
    \subfigure[PLUTO]{
      \includegraphics[scale=0.33]{figures/pdisk_020}
    }
  \end{center}
  \caption{Preliminary 3D simulations using the (a) ZEUS-MP and (b)
    PLUTO. The non-axisymmetric midplane density at the end of the run
    is shown. Here $\psi \equiv \pi/2 - \theta$ is the angular height
    from the midplane.\label{3d_prelim}}   
\end{figure}

@@

\begin{figure}
%scale=0.41
  \includegraphics[scale=.41,clip=true,trim=0cm 1cm 0cm 0cm]{figures/nonaxi_evol_ang_zeus}
  \includegraphics[scale=.41]{figures/nonaxi_evol_ang_pluto}
  \caption{Evolution of angular momentum components in the 3D 
    simulations show in Fig. \ref{3d_prelim}. The perturbation
    relative to $t=10P_0$ is shown in units of the initial total
    angular momentum $J_\mathrm{ref}$.\label{3d_prelim_angmom}} 
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/pdiskxy_020_m1}
  \caption{Cartesian plot of the $m=1$ midplane density in the PLUTO
    simulation shown in Fig. \ref{3d_prelim}.\label{pluto_cart}}   
\end{figure}
